Notes on Perturbational Quantities

### 2008-07-30 docs/pert_notes/paper.tex
caught a few typos

increase the order of accuracy, but Ann has convinced me that this term isn't necessary.}  

@@

compute $\rho_0^{(2)}$ from $\rho^n$ using advect\_base, which advances equation 

@@

that we have not called correct\_base yet, which computes  $\rho^{n+1}$ from $\rho_0^{(2)}$. 
We use $\rho^{(2)}$ rather than $\rho^{n+1}$ to construct $\rho_0^{n+\half,{\rm avg}}$ to be 

>>>>

decrease the error, but Ann has convinced me that this term isn't necessary.}  

@@

compute $\rho_0^{(2)}$ from $\rho_0^n$ using advect\_base, which advances equation 

@@

that we have not called correct\_base yet, which computes  $\rho_0^{n+1}$ from $\rho_0^{(2)}$. 
We use $\rho_0^{(2)}$ rather than $\rho_0^{n+1}$ to construct $\rho_0^{n+\half,{\rm avg}}$ to be 
